---
output:
  md_document:
    variant: gfm
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(Gtransition)
```

# Gtransition


**Estimate Natural Mortality (M) throughout the life history of species**
This package allows to...


## Installation

Install the CRAN version:

```R
install.packages("gnomonicM")
```


After, that call the package:
```R
library("Gtransition")
```


## Examples

This is a basic example which shows you how to calculate the transition growth matrix natural:

## Mean growth increment (based on von Bertalanffy equation)

```{r}
output <- mgi(lowerL = 10, classL = 10, Linf = 60, K = 0.3, method = "vonB")

output
output$delta
output$Laverage
```


## Transition growth matrix
```{r}
mat <- transitionM(lowerL = 10, classL = 10, Linf = 60, 
                   distribution = "gamma", delta = vonb$delta, beta = 1.5, sigma = NULL)

output
```

### References
Luquin-Covarrubias M., Morales-Bojorquez E. (2020). Effects of stochastic growth on population dynamics and management quantities estimated from an integrated catch-at-length assessment model: Panopea globosa as case study. Ecologial Modeling 440, 109384. https://doi.org/10.1016/j.ecolmodel.2020.109384

Sullivan P.J., Lai H., Galluci V.F. (1990). A Catch-at-Length analysis that incorporates a stochastic model of growth. Can. J. Fish. Aquat. Sci. 47: 184-198.

